---
title: "Monty Hall Simulation"
author: "Abhishu Karki"
date: "Jan 14, 2026"
format: html
knitr:
  opts_chunk:
    echo: true 
    eval: true
    message: false
    collapse: true
    warning: false 
---

# My Simulation

I began by loading the required packages.

```{r}
# Setup ------
library(tidyverse)
library(knitr)
```

My next steps are to set the stage -- creating three doors -- and to set a score sheet to track results.

```{r}
## set the stage
doors <- c('A','B','C')
##keep score 
results <- tibble(
  trial <- 1:10000
)
```

Finally I run the game. I place the prize at random, and the contestant choose a door at random. The host opens a door to reveal a goat. Then the contestants act: Marilyn switches doors while Paul does not. I repeat the game 10,000 times and record the winners in the `results` object created previously.


```{r}
for (i in 1:10000) {
car <- sample(doors, 1) #puts car behind 1 door at random
choice <- sample(doors, 1) #has a contestant choose a door
reveal <- sample(doors[doors != car & doors != choice],1) #reveals a goat the sign [ ] helps makes a condition within a value
switch <- sample(doors[doors !=choice & doors != reveal],1) #switch between the remaining door that hasn't already been chosen
results[i, 'winners'] <- if_else(car == choice, "Paul wins", "Marilyn wins")}
```

# Results
The table below presents the results of the simulation.

```{r}
outcomes <-
  results |>
  count(winners) |>
  mutate(percent = n / sum(n) *100)

kable(outcomes, caption = 'Results of simulation', digits = 1L)
```

In 10,000 simulations, the contestant who switches won a total of 'r results |> filter(winner == "Marilyn wins") |> nrow()` times. This is consistent with Marilyn's expectation. You should switch!


